Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-21 manuscript/supplemental_material.Rnw
include more go results

<<go.analysis.all.species,echo=FALSE,results="asis">>=
for (this.species in go.results[grepl("100 No Housekeeping",type) & FDR <= 0.0005,unique(species)]) {
    print(xtable(go.results[grepl("100 No Housekeeping",type) & FDR <= 0.0005 & species == this.species,
                            list(GO.ID,Term,FDR,Ontology,type)
                            ],
                 caption=paste0("Signficantly enriched ($\\mathrm{FDR}\\le0.0005$) GO terms in ",
                     "\\textit{",capfirst(this.species),"}"),
                 label=paste0("tab:go_terms_enriched_",gsub(" ","_",this.species)),
                 display=c("s","s","s","e","s","s")
                 ),
          size="\\small",
          booktabs=TRUE,
          floating=TRUE)
}
@

>>>>

<<go.analysis.all.species,echo=FALSE,results="asis">>=
for (this.species in go.results[grepl("100 No Housekeeping",type) & FDR <= 0.05,unique(species)]) {
    print(xtable(go.results[grepl("100 No Housekeeping",type) & FDR <= 0.05 & species == this.species,
                            list(GO.ID,Term,FDR,Ontology,type)
                            ][order(FDR)],
                 caption=paste0("Signficantly enriched ($\\mathrm{FDR}\\le0.05$) GO terms in ",
                     "\\textit{",capfirst(this.species),"}"),
                 label=paste0("tab:go_terms_enriched_",gsub(" ","_",this.species)),
                 display=c("s","s","s","e","s","s")
                 ),
          size="\\small",
          booktabs=TRUE,
          tabular.environment="longtable",
          caption.placement="top",
          add.to.row = list(pos = list(0),command = "\\midrule \\endhead "),
          floating=FALSE)
}
@
